\textbf{COMPARISON OF \\ HEURISTIC ALGORITHMS \\ FOR KP01} \\[0.5cm] \rule{12cm}{0.3mm} \\[0.5cm] \small \scshape{A comparison of heuristic algorithms for solving the 0-1 Knapsack Problem} \\[0.4cm] \rule{12cm}{0.3mm} \vskip -0.3cm

### 2023-04-20 doc/paper.tex
more graphs in doc

\paragraph{\textbf Solving the 0-1 Knapsack Problem}} \mbox{}\

@@

3 more testgroups of 5 testcases were made using a random number generator, where a random number was generated using the Mersenne Prime Twister (mt19937). A computer cannot generate a truly random number. A pseudorandom number is what is generated, which is a number which appears to be statistically random, but has been generated using a deterministic process. The 3 groups had item counts of 100, 1000, and 10000. The number of solutions in memory (for the heuristic algorithms) was put in the input file which was kept constant, 20, in all testcases and algorithms for this report. In the random number generated testcases, the number of items $n$ was chosen to either be 100, 1000 or 10000. The profit and weight values were then randomly generated in a range of \, $ [1, noItems] $ while a sum-of-weights variable \emph{sum} was kept. The max weight was then randomly generated in a range of $[\frac{\text{sum}}{100} , \frac{\text{sum}}{10}]$, so that the knapsack wouldn't be able to hold all the items. To avoid any overflow errors, all generated numbers (and the sum of the profit/weight values) were kept below the max value of an \emph{int} which is $2^{31}-1$ in many programming languages.  Then $n$, $W$ (maxWeight), and each item (profit and weight values) was put in an input file. To make a fair comparison the number of $ITERATIONS$ (how many times a candidate solution is generated) was set to 100 for both algorithms.

@@

Each testcase was then run on each algorithm and saved in a spreadsheet producing a csv table, refer to appendix\S.

@@

\section{Results}

\subsection{Raw Data}
Refer to the appendix for the \hypertarget{random100}{raw data} for the algorithms running on the six testgroups: 100, 1000, 10k randomized numbers respectively and 3 differently correlated datasets. 
% \href{https://github.com/raunakCode/diploma-project/blob/main/testing/algorithms%20results.csv}{\textcolor{purple}{Link to results}}

@@

\begin{table}[!h]\centering
    \caption{Randomized 100 items} \label{100-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &4160.33 &2561 &5288 &3535 &1747 \\ \hline
        Harmony StDev. &3.50 &0 &19.66 &0 &0 \\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &3926.83 &2561 &4879 &3360.66 &1711.5 \\ \hline
        BMQHOA StDev. &40.27 &0 &46.18 &68.96 &25.71 \\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h]\centering
    \caption{Randomized 1000 items} \label{1000-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &156083.83 &118603.83 &144070 &109734.33 &126366.16 \\ \hline
        Harmony StDev. &830.04 &1904.69 &1343.77 &1037.03 &1236.73 \\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &145086.5 &109876.33 &136622.66 &101951.33 &118291.16 \\ \hline
        BMQHOA StDev. &1035.45 &1540.63 &2042.95 &1271.88 &799.78 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h]\centering
    \caption{Randomized 10k items} \label{10k-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &7681910.33 &10567302 &8014906 &9347061.66&9583139.16\\ \hline
        Harmony StDev. &51555.39&23956.31&39449.15&56967.66&55816.60\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &7438487.16&10276681.83&7774520.83&9075476 &9330322.16\\ \hline
        BMQHOA StDev. &29887.17&50507.35&34559.10&53168.02&46301.35\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h]\centering
    \caption{Uncorrelated Dataset} \label{uncorrelated-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &9147 &11238 &51019.5 &99036.16&448975 \\ \hline
        Harmony StDev. &0 &0 &437.85&1544.34&1135.46\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &8974.5 &10976.5 &47401.5 &91725.83&431259.66\\ \hline
        BMQHOA StDev. &147.24&154.37&841.75&1346.23&3049.43\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h]\centering
    \caption{Weakly Correlated Dataset} \label{weakly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &1514 &1627.66&8907.33&17371.83&82681.33\\ \hline
        Harmony StDev. &0 &2.42&27.56&126.76&390.98\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &1508.16&1613.66&8435.33&16539 &80900.66\\ \hline
        BMQHOA StDev. &6.82&16.74&60.60&133.95&970.71\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h]\centering
    \caption{Strongly Correlated Dataset} \label{strongly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &2391.66&2697 &13682.5 &26444.66&126448 \\ \hline
        Harmony StDev. &6.08&0 &60.05&240.84&615.61\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &2327.33&2658.66&13334.66&25604 &123813.83\\ \hline
        BMQHOA StDev. &48.55&48.81&182.91&91.32&773.19\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

@@

\section{Appendix}
\begin{table}[!h]\centering
    \caption{Randomized 100 items} \label{random100}
    \begin{tabu}{|c|c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Optimal & 4169 & 2561 & 5309 & 3535 & 1747 \\ [-1pt] \tabucline[1pt]{1-6} 
        \multirow{6}{*}{Harmony} & 4163 & 2561 & 5254 & 3535 & 1747 \\ \cline{2-6}
        & 4163 & 2561 &5292 &3535 &1747 \\ \cline{2-6} 
        &4161 &2561 &5307 &3535 &1747 \\ \cline{2-6} 
        &4163 &2561 &5282 &3535 &1747 \\ \cline{2-6} 
        &4155 &2561 &5307 &3535 &1747 \\ \cline{2-6} 
        &4157 &2561 &5286 &3535 &1747 \\[-1pt] \tabucline[1pt]{1-6}
        \multirow{6}{*}{BMQHOA} &3895 &2561 &4952 &3398 &1734 \\\cline{2-6} 
        &3939 &2561 &4871 &3380 &1728 \\\cline{2-6} 
        &3870 &2561 &4890 &3298 &1705 \\\cline{2-6} 
        &3948 &2561 &4829 &3435 &1718 \\\cline{2-6} 
        &3984 &2561 &4832 &3255 &1663 \\\cline{2-6} 
        &3925 &2561 &4900 &3398 &1721 \\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h] \centering
    \caption{Randomized 1000 items} \label{random1000}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Optimal & 4169 & 2561 & 5309 & 3535 & 1747 \\ [-1pt] \tabucline[1pt]{1-6} 
        \multirow{6}{*}{Harmony} & 156898 & 119888 & 141878 & 110608 & 128009 \\ \cline{2-6}
        &155104 &117086 &143322 &108732 &124714 \\ \cline{2-6} 
        &155849 &117110 &145381 &108973 &125400 \\ \cline{2-6} 
        &155171 &116958 &145411 &109414 &126089 \\ \cline{2-6} 
        &156929 &118957 &143984 &109292 &126532 \\ \cline{2-6} 
        &156552 &121624 &144444 &111387 &127453 \\ [-1pt] \tabucline[1pt]{1-6}
        \multirow{6}{*}{BMQHOA} &146187 &110066 &136620 &103073 &117832 \\ \cline{2-6} 
        &146215 &107880 &133731 &101385 &117207 \\ \cline{2-6} 
        &145231 &109374 &134981 &99977 &119272 \\ \cline{2-6} 
        &143511 &108754 &137715 &102749 &117836 \\ \cline{2-6} 
        &144522 &112065 &137185 &101318 &118550 \\ \cline{2-6} 
        &144853 &111119 &139504 &103206 &119050 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h] \centering
    \caption{Randomized 10k items} \label{random10k}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Optimal &9927473 &13743791 &10286004 &12155538 &12446154 \\ [-1pt] \tabucline[1pt]{1-6} 
        \multirow{6}{*}{Harmony} &7667918 &10556718 &8064941 &9425334 &9545542 \\ \cline{2-6}
        &7738704 &10587645 &8059383 &9305736 &9547723 \\ \cline{2-6} 
        &7590747 &10523899 &7986766 &9304266 &9679149 \\ \cline{2-6} 
        &7680907 &10571613 &8018689 &9377397 &9621182 \\ \cline{2-6} 
        &7719598 &10584319 &7983856 &9386494 &9538807 \\ \cline{2-6} 
        &7693588 &10579618 &7975801 &9283143 &9566432 \\ [-1pt] \tabucline[1pt]{1-6}
        \multirow{6}{*}{BMQHOA} &7483414 &10312486 &7823273 &9090434 &9368506 \\ \cline{2-6} 
        &7398497 &10196292 &7796298 &9030552 &9332763 \\ \cline{2-6} 
        &7429280 &10328466 &7768443 &9107012 &9246868 \\ \cline{2-6} 
        &7452071 &10285331 &7786678 &9064793 &9351821 \\ \cline{2-6} 
        &7450200 &10236135 &7737071 &9006745 &9312696 \\ \cline{2-6} 
        &7417461 &10301381 &7735362 &9153320 &9369279 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

>>>>

\paragraph{\textbf Solving the 0-1 Knapsack Problem} \mbox{}\

@@

3 testgroups of 5 testcases were made using a random number generator, where a random number was generated using the Mersenne Prime Twister (mt19937). A computer cannot generate a truly random number. A pseudorandom number is what is generated, which is a number which appears to be statistically random, but has been generated using a deterministic process. The 3 groups had item counts of 100, 1000, and 10000. The number of solutions in memory (for the heuristic algorithms) was put in the input file which was kept constant, 20, in all testcases and algorithms for this report. In the random number generated testcases, the number of items $n$ was chosen to either be 100, 1000 or 10000. The profit and weight values were then randomly generated in a range of $ [1, noItems] $ while a sum-of-weights variable \emph{sum} was kept. The max weight was then randomly generated in a range of $[\frac{\text{sum}}{100} , \frac{\text{sum}}{10}]$, so that the knapsack wouldn't be able to hold all the items. To avoid any overflow errors, all generated numbers (and the sum of the profit/weight values) were kept below the max value of an \emph{int} which is $2^{31}-1$ in many programming languages.  Then $n$, $W$ (maxWeight), and each item (profit and weight values) was put in an input file. To make a fair comparison the number of $ITERATIONS$ (how many times a candidate solution is generated) was set to 100 for both algorithms.

@@

Each testcase was then run on each algorithm and saved in a spreadsheet producing a csv table, refer to appendix.

@@

\section{Not finished - Results}

\subsection{Raw Data}
Refer to the appendix for the \hyperlink{random100}{raw data} for the algorithms running on the six testgroups: 100, 1000, 10k randomized numbers respectively and 3 differently correlated datasets. 
% \href{https://github.com/raunakCode/diploma-project/blob/main/testing/algorithms%20results.csv}{\textcolor{purple}{Link to results}}

@@

\begin{table}[h!]\centering
    \caption{Mean and StDev. of 100 Randomized items} \label{100-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &4160.33 &2561 &5288 &3535 &1747 \\ \hline
        Harmony StDev. &3.50 &0 &19.66 &0 &0 \\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &3926.83 &2561 &4879 &3360.66 &1711.5 \\ \hline
        BMQHOA StDev. &40.27 &0 &46.18 &68.96 &25.71 \\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

    \vspace{1cm}

    \caption{Mean and StDev. of 1000 Randomized items} \label{1000-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &156083.83 &118603.83 &144070 &109734.33 &126366.16 \\ \hline
        Harmony StDev. &830.04 &1904.69 &1343.77 &1037.03 &1236.73 \\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &145086.5 &109876.33 &136622.66 &101951.33 &118291.16 \\ \hline
        BMQHOA StDev. &1035.45 &1540.63 &2042.95 &1271.88 &799.78 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

    \vspace{1cm}

    \caption{Mean and StDev. of 10k Randomized items} \label{10k-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &7681910.33 &10567302 &8014906 &9347061.66&9583139.16\\ \hline
        Harmony StDev. &51555.39&23956.31&39449.15&56967.66&55816.60\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &7438487.16&10276681.83&7774520.83&9075476 &9330322.16\\ \hline
        BMQHOA StDev. &29887.17&50507.35&34559.10&53168.02&46301.35\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

   % \vspace{1cm}
\begin{table}
    \centering
    \caption{Mean and StDev. of Uncorrelated Dataset} \label{uncorrelated-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &9147 &11238 &51019.5 &99036.16&448975 \\ \hline
        Harmony StDev. &0 &0 &437.85&1544.34&1135.46\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &8974.5 &10976.5 &47401.5 &91725.83&431259.66\\ \hline
        BMQHOA StDev. &147.24&154.37&841.75&1346.23&3049.43\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

    \vspace{1cm}

    \caption{Mean and StDev. of Weakly Correlated Dataset} \label{weakly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &1514 &1627.66&8907.33&17371.83&82681.33\\ \hline
        Harmony StDev. &0 &2.42&27.56&126.76&390.98\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &1508.16&1613.66&8435.33&16539 &80900.66\\ \hline
        BMQHOA StDev. &6.82&16.74&60.60&133.95&970.71\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

    \vspace{1cm}

    \caption{Mean and StDev. of Strongly Correlated Dataset} \label{strongly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &2391.66&2697 &13682.5 &26444.66&126448 \\ \hline
        Harmony StDev. &6.08&0 &60.05&240.84&615.61\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &2327.33&2658.66&13334.66&25604 &123813.83\\ \hline
        BMQHOA StDev. &48.55&48.81&182.91&91.32&773.19\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

%100 randomized items mean and stdev graph
\begin{figure}[hbt!]
\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 6,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 4160.33) +- (0,3.5)
                (2, 2561) +- (0,0)
                (3, 5288) +- (0,19.667)
                (4,3535) +- (0,0)
                (5,1747) +- (0,0)
                (6,1) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 3926.83) +- (0,40.27613023)
                (2, 2561) +- (0,0)
                (3, 4879) +- (0,46.18224767)
                (4,3360.66) +- (0,68.9627919)
                (5,1711.5) +- (0,25.71186497)
                (6,1) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
    \caption{Mean of profit values for 100 randomized items} \label{100-graph}
\end{figure}

%1000 random items mean and stdev graph
\begin{figure}[hbt!]
\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 6,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 156083.83) +- (0,830.04)
                (2, 118603.83) +- (0,1904.70)
                (3, 144070.00) +- (0,1343.77)
                (4, 109734.33) +- (0,1037.03)
                (5, 126366.17) +- (0,1236.73)
                (6,1) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 145086.50) +- (0,1035.46)
                (2, 109876.33) +- (0,1540.63)
                (3, 136622.67) +- (0,2042.95)
                (4,101951.33) +- (0,1271.88)
                (5,118291.17) +- (0,799.79)
                (6,1) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for 1000 randomized items} \label{1000-graph}
%\end{figure}

%10k random items mean and stdev graph
%\begin{figure}[hbt!]
%\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 6,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 7681910.333) +- (0, 51555.40)
                (2, 10567302) +- (0, 23956.32)
                (3, 8014906) +- (0, 39449.15)
                (4, 9347061.67) +- (0, 56967.67)
                (5, 9583139.17) +- (0, 55816.61)
                (6,1) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 7438487.17) +- (0, 29887.18)
                (2, 10276681.83) +- (0, 50507.36)
                (3, 7774520.83) +- (0, 34559.11)
                (4, 9075476.00) +- (0, 53168.02)
                (5, 9330322.17) +- (0, 46301.35)
                (6, 1) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for 10k randomized items} \label{10k-graph}
\end{figure}

%uncorrelated items mean and stdev graph
\begin{figure}[hbt!]
    \centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xmin = 1,
            xmax = 6,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            legend cell align={left},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 9147) +- (0, 0.00)
                (2, 11238.00) +- (0, 0.00)
                (3, 51019.50) +- (0, 437.85)
                (4, 99036.17) +- (0, 1544.34)
                (5, 448975.00) +- (0, 1135.46)
                (6, 0) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 8974.50) +- (0, 147.24)
                (2, 10976.50) +- (0, 154.37)
                (3, 47401.50) +- (0, 841.76)
                (4, 91725.83) +- (0, 1346.24)
                (5, 431259.67) +- (0, 3049.43)
                (6, 0) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for uncorrelated items} \label{uncorrelated-graph}
%\end{figure}

%\begin{figure}[hbt!]
    %\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xmin = 1,
            xmax = 6,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            legend cell align={left},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 1514) +- (0, 0.00)
                (2, 1627.666667) +- (0, 2.422120283)
                (3, 8907.333333) +- (0, 27.56567914)
                (4, 17371.83333) +- (0, 126.7665834)
                (5, 82681.33333) +- (0, 390.9842282)
                (6, 0) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 1508.166667) +- (0, 6.823977335)
                (2, 1613.666667) +- (0, 16.74116683)
                (3, 8435.333333) +- (0, 60.6025302)
                (4, 16539) +- (0, 133.9596954)
                (5, 80900.66667) +- (0, 970.7196643)
                (6, 0) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for weakly correlated items} \label{weakly-graph}
%\end{figure}

%\begin{figure}[hbt!]
    %\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xmin = 1,
            xmax = 6,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            legend cell align={left},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 2391.666667) +- (0, 6.08824003)
                (2, 2697) +- (0, 0)
                (3, 13682.5) +- (0, 60.05580738)
                (4, 26444.66667) +- (0, 240.8407496)
                (5, 126448) +- (0, 615.61384)
                (6, 0) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 2327.333333) +- (0, 48.55375028)
                (2, 2658.666667) +- (0, 48.81666382)
                (3, 13334.66667) +- (0, 182.9160099)
                (4, 25604) +- (0, 91.32579044)
                (5, 123813.8333) +- (0, 773.1955553)
                (6, 0) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for strongly correlated items} \label{strongly-graph}
\end{figure}

\clearpage

@@

\section{Not finished - Discussion}

\section{Appendix}
\begin{table}[!h]\centering
    \caption{Randomized 100 items} \label{random100}
    \begin{tabu}{|c|c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Optimal & 4169 & 2561 & 5309 & 3535 & 1747 \\ [-1pt] \tabucline[1pt]{1-6} 
        \multirow{6}{*}{DGHS} & 4163 & 2561 & 5254 & 3535 & 1747 \\ \cline{2-6}
        & 4163 & 2561 &5292 &3535 &1747 \\ \cline{2-6} 
        &4161 &2561 &5307 &3535 &1747 \\ \cline{2-6} 
        &4163 &2561 &5282 &3535 &1747 \\ \cline{2-6} 
        &4155 &2561 &5307 &3535 &1747 \\ \cline{2-6} 
        &4157 &2561 &5286 &3535 &1747 \\[-1pt] \tabucline[1pt]{1-6}
        \multirow{6}{*}{BMQHOA} &3895 &2561 &4952 &3398 &1734 \\\cline{2-6} 
        &3939 &2561 &4871 &3380 &1728 \\\cline{2-6} 
        &3870 &2561 &4890 &3298 &1705 \\\cline{2-6} 
        &3948 &2561 &4829 &3435 &1718 \\\cline{2-6} 
        &3984 &2561 &4832 &3255 &1663 \\\cline{2-6} 
        &3925 &2561 &4900 &3398 &1721 \\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h] \centering
    \caption{Randomized 1000 items} \label{random1000}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Optimal & 4169 & 2561 & 5309 & 3535 & 1747 \\ [-1pt] \tabucline[1pt]{1-6} 
        \multirow{6}{*}{DGHS} & 156898 & 119888 & 141878 & 110608 & 128009 \\ \cline{2-6}
        &155104 &117086 &143322 &108732 &124714 \\ \cline{2-6} 
        &155849 &117110 &145381 &108973 &125400 \\ \cline{2-6} 
        &155171 &116958 &145411 &109414 &126089 \\ \cline{2-6} 
        &156929 &118957 &143984 &109292 &126532 \\ \cline{2-6} 
        &156552 &121624 &144444 &111387 &127453 \\ [-1pt] \tabucline[1pt]{1-6}
        \multirow{6}{*}{BMQHOA} &146187 &110066 &136620 &103073 &117832 \\ \cline{2-6} 
        &146215 &107880 &133731 &101385 &117207 \\ \cline{2-6} 
        &145231 &109374 &134981 &99977 &119272 \\ \cline{2-6} 
        &143511 &108754 &137715 &102749 &117836 \\ \cline{2-6} 
        &144522 &112065 &137185 &101318 &118550 \\ \cline{2-6} 
        &144853 &111119 &139504 &103206 &119050 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h] \centering
    \caption{Randomized 10k items} \label{random10k}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Optimal &9927473 &13743791 &10286004 &12155538 &12446154 \\ [-1pt] \tabucline[1pt]{1-6} 
        \multirow{6}{*}{DGHS} &7667918 &10556718 &8064941 &9425334 &9545542 \\ \cline{2-6}
        &7738704 &10587645 &8059383 &9305736 &9547723 \\ \cline{2-6} 
        &7590747 &10523899 &7986766 &9304266 &9679149 \\ \cline{2-6} 
        &7680907 &10571613 &8018689 &9377397 &9621182 \\ \cline{2-6} 
        &7719598 &10584319 &7983856 &9386494 &9538807 \\ \cline{2-6} 
        &7693588 &10579618 &7975801 &9283143 &9566432 \\ [-1pt] \tabucline[1pt]{1-6}
        \multirow{6}{*}{BMQHOA} &7483414 &10312486 &7823273 &9090434 &9368506 \\ \cline{2-6} 
        &7398497 &10196292 &7796298 &9030552 &9332763 \\ \cline{2-6} 
        &7429280 &10328466 &7768443 &9107012 &9246868 \\ \cline{2-6} 
        &7452071 &10285331 &7786678 &9064793 &9351821 \\ \cline{2-6} 
        &7450200 &10236135 &7737071 &9006745 &9312696 \\ \cline{2-6} 
        &7417461 &10301381 &7735362 &9153320 &9369279 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[!h] \centering
    \caption{Uncorrelated Dataset} \label{uncorrelated}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Optimal &9147 &11238 &54503 &110625 &563647 \\ [-1pt] \tabucline[1pt]{1-6} 
        \multirow{6}{*}{DGHS} &9147 &11238 &51166 &100770 &450386 \\ \cline{2-6}
        &9147 &11238 &50911 &98217 &448025 \\ \cline{2-6} 
        &9147 &11238 &50674 &100153 &449887 \\ \cline{2-6} 
        &9147 &11238 &51168 &100285 &447368 \\ \cline{2-6} 
        &9147 &11238 &51720 &97570 &448856 \\ \cline{2-6} 
        &9147 &11238 &50478 &97222 &449328 \\ [-1pt] \tabucline[1pt]{1-6}
        \multirow{6}{*}{BMQHOA} &8990 &11005 &47569 &91878 &429245 \\ \cline{2-6} 
        &9147 &11031 &47106 &90966 &437054 \\ \cline{2-6} 
        &8911 &10759 &47773 &93434 &432253 \\ \cline{2-6} 
        &9147 &11168 &47302 &91491 &429942 \\ \cline{2-6} 
        &8810 &10826 &48608 &89694 &429823 \\ \cline{2-6} 
        &8842 &11070 &46051 &92892 &429241 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}
